Poseidon Adventure

### 2020-10-22 NOBAmsdiets.Rmd
add fish wt age, ann age, ann wt age

@@

#### Survey age composition (annual ages)
```{r plot-annagecomp, eval=FALSE}
#read in comp data
annage_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "survObsFullAgeComp.rds")))
annage_comp_data <- annage_comp_data[[1]]

#fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsAgeComp.rds")))
#fish_age_comp <- fish_age_comp[[1]]

#add this to om_indices function so that this has years when read in
#fish_age_comp$time <- as.integer(floor(fish_age_comp$time/fstepperyr))

Natage <- filter(annage_comp_data, time %in% c(150:270))

Natageplot <- ggplot(Natage, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          Natage$species))

  Natageplot + facet_wrap(~time/stepperyr, ncol=6, scales="free_y")
```

#### Survey iterpolated weight at age (annual ages) 
```{r plot-annwtage, eval=FALSE}

wtage <- readRDS(file.path(d.name, paste0(scenario.name, "survObsFullWtAtAge.rds")))
wtage <- wtage[[1]] #this still has second list component, diagnostic plot
wtage <- wtage[[1]]

wageplot <- ggplot(wtage, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year sample"))

wageplot + facet_wrap(c("species"), scales="free_y")

#### Fishery catch at age (annual ages)
```{r plot-catchagecomp, eval=FALSE}

@@

Catage <- filter(fish_annage_comp, time %in% c(30:53))

Catageplot <- ggplot(Catage, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          Catage$species))

  Catageplot + facet_wrap(~time, ncol=6, scales="free_y")
```

#### Fishery iterpolated weight at age (annual ages) 
```{r plot-fishannwtage, eval=FALSE}

wtage <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullWtAtAge.rds")))
wtage <- wtage[[1]] #this still has second list component, diagnostic plot
wtage <- wtage[[1]]

wageplot <- ggplot(wtage, aes(time, atoutput)) +
  geom_line(aes(colour = factor(agecl))) +
  theme_tufte() +
  theme(legend.position = "bottom") +
  xlab("model timestep (5 per year)") +
  ylab("average individual weight (g)") +
  labs(subtitle = paste0(scenario.name, " annual mid year sample"))

wageplot + facet_wrap(c("species"), scales="free_y")

>>>>

#### Fishery weight at age (age classes)
```{r}
fishwtage <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsWtAtAge.rds")))
fishwtage <- fishwtage[[1]]

wageplot(fishwtage)

@@

#### Survey age composition (annual ages)
```{r plot-annagecomp, results="asis"}

# annage_comp_data read in above, apply plot function, quit hardcoding survey names

for(s in names(annage_comp_data)){
  cat("  \n##### ",  s,"  \n")
  acompsub <- as.data.frame(annage_comp_data[[s]][[1]]) %>% filter(time %in% c(150:270)) %>%
    group_by(species) %>%
    group_map(~ Natageplot(.x), keep = TRUE)

  for(i in 1:length(acompsub)) {
    print(acompsub[[i]])
  }
  cat("  \n")
}
```

#### Survey iterpolated weight at age (annual ages) 
```{r plot-annwtage, results='asis'}

# annage_wtage read in above 
# wtage <- wtage[[1]] #this still has second list component, diagnostic plot
# wtage <- wtage[[1]]

for(s in names(annage_wtage)){
  cat("  \n##### ",  s,"  \n")
  print(wageplot(annage_wtage[[s]][[1]][[1]]))
  cat("  \n")
}
```

#### Fishery catch at age (annual ages)
```{r plot-catchagecomp}

@@

acompsub <- as.data.frame(fish_annage_comp) %>% filter(time %in% c(30:54)) %>%
  group_by(species) %>%
  group_map(~ Natageplot(.x), keep = TRUE)

#### Fishery iterpolated weight at age (annual ages) 
```{r plot-fishannwtage}

fish_annage_wtage <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullWtAtAge.rds")))

wageplot(fish_annage_wtage[[1]][[1]])

### 2020-10-22 docs/index.Rmd
testing diet functions, plotting output
compare with biomass_eaten
add fish wt age, ann age, ann wt age

>>>>

### Full age structured data for multispecies modeling, June-October 2020

<a href="https://sgaichas.github.io/poseidon-dev/NOBAmsdiets.html" target="_blank">Explore NOBA diet comps and multi-survey multispecies wrappers, October 21, 2020</a>

Including detailed diet exploration, multiple surveys, survey function bug fixes for species with < 10 cohorts.
